\startcomponent *

\product  prd-analysis


\startchapter [title={Convergence of sequences and series}, reference=chp:convergence]

	\startitemize [1, nowhite, after]
		\item  We can only talk of \emph{convergence of sequences} in \emph{Hausdorff topological spaces}.
		\item  We can only talk of \emph{series} in \emph{commutative groups}, because we need + to be defined.
		\item  We can only talk of \emph{convergence of series} in \emph{commutative Hausdorff topological groups}.
		\item  We can only talk of \emph{absolute convergence of series} in \emph{normed commutative Hausdorff topological groups}.
		\item  This is from \goto{Wikipedia}[url(https://en.wikipedia.org/wiki/Series_(mathematics)#Calculus_and_partial_summation_as_an_operation_on_sequences)]. Let \m{S} be the vector space of sequences. Then the partial summation \m{∑: S → S, (a_n) ↦ \brnd{∑_{j = 1}^n a_j}} is a \emph{linear operator} on \m{S}, whose inverse is the finite difference operator, \m{Δ}. These behave as discrete analogs of integration and differentiation, only for series (functions of a natural number) instead of functions of a real variable. For example, the sequence \m{\brnd{1, 1, 1, …}} has series \m{\brnd{1, 2, 3, …}} as its partial summation, which is analogous to the fact that \m{∫_0^x 1 \,\d t = x}.
		\item  Classification of convergence of series
		\startitemize [n, nowhite, after]
			\item  Pointwise or uniform convergence
			\item  Absolute, unconditional and conditional convergence
				\startitemize [1, nowhite, after]
					\item  \emph{Absolute convergence} means \m{∑ \norm{a_n} < ∞}.
					\item  \emph{Unconditional convergence} means all rearrangements of the series are convergent to the same value. That is, if \m{σ: ℕ → ℕ} is a permutation, then \m{∑_n a_n = ∑_n a_{σ(n)}}.

						In complete spaces, absolute convergence ⟹ unconditional convergence, but the converse is not true in general. In finite dimensional spaces, the converse is true by Riemann rearrangement theorem. But the Dvoretzky--Rogers theorem asserts that every in infinite-dimensional Banach space admits an unconditionally convergent series that is not absolutely convergent. (see \goto{this Wikipedia article}[\url(https://en.wikipedia.org/wiki/Absolute_convergence#Rearrangements_and_unconditional_convergence)])
					\item  \emph{Conditional convergence} means convergent but not absolutely convergent.
				\stopitemize
			\item  Depending on the space of values, for example, real number, arithmetic progression, trigonometric function, etc.
		\stopitemize
	\stopitemize

\stopchapter


\startchapter [title={Differentiation}, reference=chp:differentiation]

	\startsection [title={Differentiation of functions with real powers}]
		This idea is by Prof Sundar.

		For each \m{n ∈ ℕ}, we can differentiate \m{f: ℝ → ℝ: x ↦ x^n} using the limit definition of the derivative, by using the factorization \m{(x + h)^n - x^n = (x + h - x) ∑_{j = 0}^{n - 1} h^j x^{n-1-j}}, which gives
		\startformula
			f'(x)  =  \lim_{h → 0} \frac{f(x + h) - f(x)}{h}
				=  \lim_{h → 0} ∑_{j = 0}^{n - 1} (x+h)^j x^{n-1-j}
				=  ∑_{j = 0}^{n - 1} x^j x^{n-1-j}
				=  (n-1) x^{n-1} .
		\stopformula
		But this does not work for exponents \m{r ∈ ℝ} in general. How can we do it?

		One needs to think outside the box for this. We cannot go by definition here. We note that \m{x^r = e^{r \log x}}. Now use chain rule.
	\stopsection

	\startsection [title={Example of \m{f ∈ C^∞ ∖ C^ω}}]
		How does one construct an example of a function which is smooth but not analytic? The idea is to find \m{f ≠ 0} such that \m{f^{(n)}(0) = 0 \ ∀n}.

		Note that the graph of \m{x ↦ x^n} around \m{x = 0} become flatter and flatter as \m{n → ∞}. Consider \m{f: ℝ → ℝ: x ↦ e^{-\frac{1}{x}} 𝟙_{x > 0}(x)}. Then \m{f'(x) = \frac{1}{x^2} e^{-\frac{1}{x}} 𝟙_{x > 0}(x)} (do the computations separately for \m{x > 0} and \m{x = 0}). In this way, \m{f'(0) = 0}. Continuing, we see that \m{f^{(n)}(0) = 0 \ ∀n}. Therefore, the sum \m{∑_n \frac{f^{(n)}(0)}{n!} x^n} converges to 0, which is not the same as \m{f}.

		See also \goto{this Wikipedia article}[url(https://en.wikipedia.org/wiki/Non-analytic_smooth_function)].
	\stopsection

	\startsection[title={Taylor series for multivariate functionals}, reference=sec:taylor]

		\starttheorem[title={Taylor}]
			Let \m{Ω ⊆ ℝ^d} be an open set and \m{f: Ω → ℝ} be an infinitely differentiable function at the point \m{p ∈ Ω}. Then the Taylor series of \m{f} around \m{p} for \m{v ∈ T_p Ω} is given by
			\startformula
				T(p + v)  =  ∑_{n = 0}^∞  \frac{1}{n!} \brnd{{\inn{v, \D_v}}^n f}(p) ,
				\quad \text{ where }  \inn{v, \D_v} = ∑_{j=1}^d v_j \frac{∂}{∂ v_j} .
			\stopformula
		\stoptheorem

		\startproof
			Is this a \m{ℝ} life, or is this just \m{i}maginary, caught in a landslide, no escape from \m{ℂ}. Open your eyes, look up to the sky and see. I'm trivial come, trivial go, little high, little low.

			ToDo, really!
		\stopproof

		In the differential form, this becomes
		\startformula
			\d T(p)  =  ∑_{n = 1}^∞  \frac{1}{n!} \brnd{\inn{\d v, \D_v}^n f}(p)
		\stopformula

		There is another form with multi-indexes. But the above form seems way more natural to me. See more in \goto{this}[url(https://en.wikipedia.org/wiki/Taylor_series\#Taylor_series_in_several_variables)] and \goto{this}[url(https://en.wikipedia.org/wiki/Taylor's_theorem\#Taylor's_theorem_for_multivariate_functions)] Wikipedia articles.
	\stopsection

\stopchapter

\stopcomponent
